Implementing simplified INLA into `aghq`

### 2022-11-07 src/dev_sinla/sinla.Rmd
Calculate p(x_1 = x_test_value | y) looping over z

Now we want to evaluate
$$
\tilde p(x_i \, | \, y) &= \sum_z \tilde p_\text{G}(x_i \, | \, \theta(z), y) \tilde p_\text{LA}(\theta(z) \, | \, y) w_k(z).
$$
To start with, let's evaluate this for the first value of $z$ (actually I don't really know what $z$ runs over, but this is just the first weight):

```{r}
x_test_value <- 0

z <- 1
i <- 1

#' This is the weight, w_k(z)
modesandhessians$weights[z]

#' This is the normalised Laplace approximation to log(p(theta | y))
theta <- as.numeric(modesandhessians[z, thetanames])
- h_norm(theta)

#' This is the normalised Gaussian approximation to log(p(x_i | theta, y))
#' Let's say that we're doing i = 1 (corresponding to x_i)
mean_i <- as.numeric(modesandhessians$mode[[z]][i])
Sigma <- solve(modesandhessians$H[[z]])
sd_i <- as.numeric(sqrt(Sigma[i, i]))

dnorm(x_test_value, mean = mean_i, sd = sd_i, log = TRUE)

#' So the value we would compute, on the log scale, is
dnorm(x_test_value, mean = mean_i, sd = sd_i, log = TRUE) + (- h_norm(theta)) + log(modesandhessians$weights[z])
```

Remember that we're dealing with the logarithm versions, so let's exp-sum-log for the part inside the sum:
$$
\exp \left( \log\tilde p_\text{G}(x_i \, | \, \theta(z), y) + \log \tilde p_\text{LA}(\theta(z) \, | \, y) + \log w_k(z) \right)
$$

>>>>

Now we want to evaluate
$$
\tilde p(x_i \, | \, y) = \sum_z \tilde p_\text{G}(x_i \, | \, \theta(z), y) \tilde p_\text{LA}(\theta(z) \, | \, y) w_k(z).
$$

If you wanted to evaluate this to obtain each marginal then it would be something like (pseudo-code):

```{r eval=FALSE}
for(i in 1:n) {
  for(x in x_vals) {
    for(z in z_vals) {
      #' ...
    }
  }
}
```

To start with, let's evaluate this for `i = 1`, `x = x_test_value` and the first value of `z` (actually I don't really know what $z$ runs over, but this is just the first weight):

```{r}
x_test_value <- 0
z <- 1
i <- 1
```

The weight $w_k(z)$ is:

```{r}
modesandhessians$weights[z]
```

The normalised Laplace approximation $\tilde p_\text{LA}(\theta(z) \, | \, y)$ is:

```{r}
theta <- as.numeric(modesandhessians[z, thetanames])
- h_norm(theta)
```

The normalised Gaussian approximation $p_\text{G}(x_i \, | \, \theta(z), y)$ on the log-scale is:

```{r}
mean_i <- as.numeric(modesandhessians$mode[[z]][i])
Sigma <- solve(modesandhessians$H[[z]])
sd_i <- as.numeric(sqrt(Sigma[i, i]))

dnorm(x_test_value, mean = mean_i, sd = sd_i, log = TRUE)
```

So, putting it together, the value we would compute on the log-scale is as follows:

```{r}
dnorm(x_test_value, mean = mean_i, sd = sd_i, log = TRUE) + (- h_norm(theta)) + log(modesandhessians$weights[z])
```

To obtain the unlogged version we can use:
$$
\exp \left( \log\tilde p_\text{G}(x_i \, | \, \theta(z), y) + \log \tilde p_\text{LA}(\theta(z) \, | \, y) + \log w_k(z) \right)
$$

```{r}
exp(dnorm(x_test_value, mean = mean_i, sd = sd_i, log = TRUE) + (- h_norm(theta)) + log(modesandhessians$weights[z]))
```

Great -- now let's put it together and sum over `z` so that we can obtain the probability for our `x_test_value` in marginal `i`.
We won't worry about inefficient R for loops for the time being.

```{r}
pdf <- 0

for(z in 1:length(modesandhessians$weights)) {
  theta <- as.numeric(modesandhessians[z, thetanames])
  mean_i <- as.numeric(modesandhessians$mode[[z]][i])
  Sigma <- solve(modesandhessians$H[[z]])
  sd_i <- as.numeric(sqrt(Sigma[i, i]))
  pdf <- pdf + exp(dnorm(x_test_value, mean = mean_i, sd = sd_i, log = TRUE) + (- h_norm(theta)) + log(modesandhessians$weights[z]))
}

pdf
```

Using a `fine_grid` set of values for `x_vals` for each `i` might be overly computationally expensive.
Instead what we can do is perform another separate AGHQ to select a set of `x_vals`.
To do this with the `aghq` R package, we could create a `TMB` template to evaluate $\tilde p(x_i \, | \, y)$, but I imagine this might be too annoying.
Instead, we could create the `ff` object (with components `ff$fn`, `ff$gn` `ff$hn`) in R directly.
